Insert the article title here

### 2020-07-24 tex/results.tex
Add ellis results explanation

 \begin{table}
    \centering
    \label{tab:err_AR}
    \caption{Percentage error for different aspect ratios.} 
    \begin{tabular}{c c}
    \hline%\toprule
    ARR & \% error \\
    \hline%\midrule
     $1$ & $0.95$ \\
     $2$ & $0.67$ \\
     $3$ & $0.35$ \\
     $4$ & $0.16$ \\
     $5$ & $0.72$ \\
     $6$ & $1.20$ \\
     $7$ & $1.59$ \\
    \hline%\bottomrule
    \end{tabular}
\end{table}

\pygbe AR=4 attempt of validation Figure 2a (see Figure \ref{fig:pygbe_vs_exp_2a})

\begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{pygbe_vs_exp_fig2a_Ellis.pdf} 
    \caption{\pygbe vs experiments, figure 2a of Ellis 2016. Ellis et al 
    has near field interaction in its experiments. Ellis data was digitized
    with web digitizer.}
    \label{fig:pygbe_vs_exp_2a}
 \end{figure}

First order approximation to achieve validation. In our code we do not have near 
field interaction. From Figure S4 in supplementary material of Ellis et al. We know that 
for the first mode ($E_{100}$) the difference between interaction and no interaction is 
12.17 $cm^{-1}$ (obtained from digitized data). If we use this as a first order approximation,
we can subtract that value from our curve, and the results are in Figure \ref{fig:val_2a}

>>>>

 \begin{table}
    \centering
    \caption{Percentage error for different aspect ratios.} 
    \label{tab:err_AR}
    \begin{tabular}{c c}
    \hline%\toprule
    AR & \% error \\
    \hline%\midrule
     $1$ & $0.95$ \\
     $2$ & $0.67$ \\
     $3$ & $0.35$ \\
     $4$ & $0.16$ \\
     $5$ & $0.72$ \\
     $6$ & $1.20$ \\
     $7$ & $1.59$ \\
    \hline%\bottomrule
    \end{tabular}
\end{table}

\subsubsection{Validation of \pygbe against Fig 2a experimental results}

For the case of aspect ratio four (AR=4) we obtain the smallest error using the uniform
mesh. Since we count with the mesh provided by the authors, and knowing that our computation 
for the mode $E^{\parallel}_{100}$ compares well with their computations, we attempted to 
validate our simulations with their experimental results (red curve on paper), as well 
as to replicate their simulations (green curve on paper) on Figure 2a of their paper.
Figure 2a of Ellis et al, presents measured and simulated reflectance of SiC pillar
arrays with a 500 nm gap. All their measurements and simulations were performed with 
22$^\circ$ off-normal angle of incidence and incoming polarization parallel to the 
elongated size of the pillar.

Using \pygbe we compute the extinction cross section of an isolated SiC pillar (AR=4)
with no substrate, submerged in air under a constant electric field in the z-direction, 
and rotate the orientation of the pillar to match the angle of incidence. 
(SHOULD PROBABLY PUT A DIAGRAM OF THIS). In Figure \ref{fig:pygbe_vs_exp_2a} we present 
comparison of our simulations and the experimental results from Ellis et al. There is a 
difference in the peaks wavelength that is noticeable. This could be attributed to the
fact that in their experiments the separation between pillars is of 500 nm, which implies
there are coupling effects that in our simulations are not contemplated.

\begin{figure}
    \centering
    \includegraphics[width=0.85\textwidth]{pygbe_vs_exp_fig2a_Ellis.pdf} 
    \caption{\pygbe vs experiments of figure 2a of Ellis 2016. Ellis data 
    was digitized with web digitizer.}
    \label{fig:pygbe_vs_exp_2a}
 \end{figure}

\paragraph{First order correction}

Since our simulations do not count for coupling effects, we can not strictly imitate 
the conditions to validate our solver. However, from Figure S4 on the supplementary 
material of Ellis et al, we know that coupling effects affect the $E^{\parallel}_{100}$ 
mode by a shift of 12.17 cm$^-1$. Therefore as a \textit{first order correction} we can 
subtract this value from our simulations, to contemplate for coupling effects. In Figure 
\ref{fig:val_2a} we present the result after applying the correction for coupling effects.
